IGRINS spectra of \name

### 2016-03-25 document/ms.tex
Some improvements to the manuscript, Approach 1 section of Methodology.

\newcommand{\iancze}{{\sc C15}}

@@

We modified the \iancze spectral inference framework to fit $\vM$ in each spectral order \emph{independently}: $\vT \rightarrow \vT_o$, where $o$ signifies the spectral order, which could stem from multiple spectrographs, each with multiple orders.  This change does not represent reality: the star has a single set of stellar properties, which do not depend on the wavelength range at which they are measured.  The naive single-component fit to different wavelength chunks conveys information about

\begin{eqnarray} \label{eqn:scaling}
\vM(\vT_o) &=& \vM(\vt_{\ast}, \vt_{\rm ext}) \\
         &=& \vM(\vt_{\ast}, \sigma_v, v\sin{i}, v_r) \times \Omega \times 10^{-0.4\,A_{\lambda}}, \nonumber
\end{eqnarray}

star spot areal coverage fraction is very small, then the signal associated with the

>>>>

\newcommand{\iancze}{{\sc C15 }}

@@

We modified the \iancze spectral inference framework to fit $\vM$ in each spectral order \emph{independently}: $\vT \rightarrow \vT_o$, where $o$ signifies the spectral order, which could stem from multiple spectrographs, each with multiple orders.  This change does not represent reality: the star has a single set of stellar properties, which do not depend on the wavelength range at which they are measured.  The na\"ive single-component fit to different wavelength provide a plausibility argument for the presence of a second photospheric component if the derived $\vT_o$ show a spread in $\teff$.  It is conceivable that other parameters, like $\logg$ could show a dependence on wavelength if non-standard physics---\emph{i.e.}physics not included in the pre-computed model grid---mimics the effect of \emph{e.g.} $\logg$ on the spectrum.  For example, magnetic fields could cause Zeeman broadening, which could alter the derived stellar parameters $\vT_o$.  For these reasons, we intentionally allowed \emph{all} the stellar parameters $\vT_o = \{T_{\mathrm{eff},o}, \log{g_o}, \Z_o, \sigma_{v, o}, v\sin{i}_o, v_{r,o}\}$ to vary by order.

In principle, one could refine the inference on $T_{\mathrm{eff},o}$ in an \emph{empirical Bayes'} strategy CITE (XX, astroML book?), in which we re-evaluate $\vT_o$ by setting priors on all the stellar parameters except $T_{\mathrm{eff},o}$.  We elected not to pursue an empirical Bayes' approach.

As a side benefit, the strategy of fitting $\vT_o$ in each spectral order provides a useful check on our instrumental calibration. If the stellar parameters in one order are routinely discrepant, we can examine and refine our instrumental calibration for that spectral order.  For example, the radial velocity $v_r$ could be systematically offset in one order due to instrumental calibration problems.  Or perhaps the $v\sin{i}$ could show a dependence on wavelength, since the spectral inference framework from \iancze assumes the spectral resolution is fixed across all wavelengths, but typical spectrographs exhibit a small dependence of spectral resolution on wavelength.

Spectral-order level granularity in fit quality is not available in a fit that includes all $N_{order}$ spectral orders.  In fact, the benefits of spectral chunking could be made \emph{even more granular} by chunking the spectrum into individual spectral lines or line-groups.  The fit quality could then be assessed on a line-by-line basis, even taking into account systematic effects like individual elemental abundance patterns beyond the coarse $\Z$ estimates.  Future improvements to the spectral inference framework are directed at implementing this spectral-line chunking strategy.
